
During this coursework, a lot of attention was provided to the creation of roads based on given inputs. Such a model requires to simplify reality. Thus, during my project, I made some simplification, definition, and hypothesis. My first definition of road is the following : A road is a couple of elements. The first element is an n-uple of straight lines, and the second one a n-uple of curves, such that every ending point of a straight line is connected to the starting point of another straight line through a curvature. This definition is close to how real roads are build : a sequence of straight lines and curves. My definition evolved through my work, and I’ll explain it bit by bit.
\newline
\newline
A deeper purpose of being able to model roads is to be capable to generate roads based on a road map dataset. To do so, it is necessary to find a way create an approximation of the real roads expressed through the dataset with “simplified roads” . This is the reverse-engineering part of my work : trying to understand what the real road interchange looks like only by using the road map dataset. That is the other main goal of this coursework.
\newline
\newline
This project involves programming, geometry and algebra, which are subjects that I’m particularly interested in. I decided during this semester homework to use Python as the programming language. Roads were generated visually by using a collection of “pyplot  functions” from the library matplotlib [4]. To a lesser extent, the  "math", "numpy", and "scipy" libraries have been used. During this project, I was able to generate roads as sequences of straight lines and portion of arc of circles. Then, I created two different algorithms for that : the first one has for input coordinates of circles of curvatures, their radiuses, and additional necessary residual information (I will explain this later). The second one generates arcs of circle with a constant radius, and has for input a starting point, lengths of lines, a radius, and angles for the curvatures. Then, I coded an attempt of reverse-engineering process: Using linear regression to detect straight line of the road. Within the scope of the coursework, I deem the modelling problem solved, but the reverse-engineering problem is not enough conclusive and incomplete.